Impact of Context in the Perception of a Robot

### 2015-07-02 main.tex
Fixed spacing of macros

\newcommand{\anti}{{$\mathcal{A}_0$ }}
\newcommand{\antf}{{$\mathcal{A}_1$ }}
\newcommand{\deltaant}{{ $\Delta_{\mathcal{A}_0,\mathcal{A}_1}$ }}

@@

We ran first a pilot study with 10 participants, followed by an experiment with
57 subjects (mean age: 20.9, $SD=3.9$, 32 females and 25 males).
The participants were recruited amongst students of our university. To avoid
students with a high familiarity with robots and artificial intelligent systems,
Computer Science and Electronics curriculum were excluded. This was \textit{a
posteriori} comforted by the questionnaire responses: no participants
reported itself as being very familiar with robots, 8 reported some familiarity
and 7 out of 57 owned a domestic robot (vacuum cleaner).

@@

As stated previously, the study follows a 2$\times$2 design
(table~\ref{table:design}): the \emph{deep} \vs {shallow cognitive context}
condition was between-subject ( 31 subjects performed the \emph{deep cognitive}
tasks while 26 were in the \emph{shallow cognitive} condition); the \emph{robot}
\vs \emph{human} condition was within-subject (the order of stimuli presentation
was counter-balanced over the 57 participants).

@@

We collected the gazes falling into one of these 10 zones and normalized them to
account for different total video duration and surface of AOIs between the robot
and human conditions. We finally analyzed their distribution, producing what we
call \emph{gaze patterns}.

@@

Based on the experiments conducted on 57 participants in the human
($\mathcal{H}$) and robot ($\mathcal{R}$) interactions across \emph{shallow} and
\emph{deep cognitive context} conditions, we have the following
results.\footnote{The
detailed statistics and code used for obtaining the results are available here :
\url{https://github.com/chili-epfl/anthropomorphism-eyetracking}.}

@@

Participants were asked in the post-questionnaire whether the video presented a
\emph{``robot kind of task''} or a \emph{``human kind of task''} on a 5-points
scale (numerical values ranging from -2 to 2, where -2 refers to robot kind of
task). As can be seen in figure 2, we got a significant correlation in this
manipulation check ($F[1,36] = 20.42, p < .01$) which validates our manipulation
and supports \h{0}: the participants that were shown the \emph{shallow cognitive
context} videos identified the task as more robot-like and participants watching
\emph{deep cognitive context} videos perceived the tasks as more human-like.

@@

{\sf head}: the fixations on the head for the human video
were observed to more than that for the robot video ($F[1,36] = 6.60, p < .05$)

{\sf arms}: the fixations on the arms for the $\mathcal{H}$ video
were also greater than that for the robot video ($F[1,36] = 18.65, p < .01$)

{\sf legs}: the fixations on the legs were much lower
for the human video as compared to the robot video ($F[1,36] = 2.89, p < .1$)

{\sf torso}: the fixations on the torso were higher for the
human video than for the robot video ($F[1,36] = 3.54, p < .1$)

@@

We got a significant correlation between $\delta_{\mathcal{H},\mathcal{R}}$ and
the \anti. As can be seen in figure~\ref{h2}, there is a significant negative
correlation between the two quantities (Pearson Correlation Coefficient = -0.42,
$p < .01$).

@@

Based on ANOVA results, taking the 5 groups of AOIs {\sf head}, {\sf arms}, {\sf
hands}, {\sf torso}, {\sf legs} for the robot in both the shallow and deep
cognitive context conditions, the fixations on the head in the deep condition
were found to be significantly higher than that in the shallow condition
($F[1,36] = 4.55, p < .05$). For all other AOIs groups, the fixations across
shallow and deep conditions were almost the same. Figure~\ref{h3} shows the
distribution of proportion of time spent gazing on the 5 AOIs for the two
conditions.

@@

Running an ANOVA against the evolution of anthropomorphic attributions
(\deltaant) over the duration of the experiment, in the two cognitive
conditions, shows that \deltaant is greater for tasks with a deeper cognitive
context than that for the shallow cognitive tasks ($F[1,36] = 6.54, p < .05$,
figure~\ref{h4}). In other words, after being exposed to short videos of a robot
performing simple tasks, subjects primed with a deeper cognitive context report
a significantly higher tendency to anthropomorphize robots \emph{in general} (as
the questionnaires on anthropomorphic attributions explicitely refered to
\emph{robots in general}).

>>>>

\newcommand{\anti}{{$\mathcal{A}_0$\xspace}}
\newcommand{\antf}{{$\mathcal{A}_1$\xspace}}
\newcommand{\deltaant}{{ $\Delta_{\mathcal{A}_0,\mathcal{A}_1}$\xspace}}

@@

We ran first a pilot study with 10 participants, followed by an experiment with
56 subjects (mean age: 20.9, $SD=3.9$, 31 females and 25 males).
The participants were recruited amongst students of our university. To avoid
students with a high familiarity with robots and artificial intelligent systems,
Computer Science and Electronics curriculum were excluded. This was \textit{a
posteriori} comforted by the questionnaire responses: no participants
reported itself as being very familiar with robots, 8 reported some familiarity
and 7 out of 56 owned a domestic robot (vacuum cleaner).

@@

As stated previously, the study follows a 2$\times$2 design
(table~\ref{table:design}): the \emph{deep} \vs {shallow cognitive context}
condition was between-subject ( 30 subjects performed the \emph{deep cognitive}
tasks while 26 were in the \emph{shallow cognitive} condition); the \emph{robot}
\vs \emph{human} condition was within-subject (the order of stimuli presentation
was counter-balanced over the 56 participants).

@@

We recorded the fixations on one of these 10 zones and normalized by different total video duration and surface of AOIs between the robot and human conditions. We finally analyzed their distribution, producing what we
call \emph{gaze patterns}. The difference in the gaze patterns over ``N'' AOis can be calculated as follows:\\

$ \frac{\sum_{AOI=1}^{N}\left | \frac{Time_{Human}^{i}}{Area_{Human}^{i}} - \frac{Time_{Robot}^{i}}{Area_{Robot}^{i}} \right |}{N}$

@@

Based on the experiments conducted on 55 participants in the human
($\mathcal{H}$) and robot ($\mathcal{R}$) interactions across \emph{shallow} and
\emph{deep cognitive context} conditions, we have the following
results.\footnote{The
detailed statistics and code used for obtaining the results are available here :
\url{https://github.com/chili-epfl/anthropomorphism-eyetracking}.}

@@

Participants were asked in the post-questionnaire whether the video presented a
\emph{``robot kind of task''} or a \emph{``human kind of task''} on a 5-points
scale (numerical values ranging from -2 to 2, where -2 refers to robot kind of
task). As can be seen in figure 2, we got a significant correlation in this
manipulation check ($F[1,54] = 29.0, p < .001$) which validates our manipulation
and supports \h{0}: the participants that were shown the \emph{shallow cognitive
context} videos identified the task as more robot-like and participants watching
\emph{deep cognitive context} videos perceived the tasks as more human-like.

@@

{\sf head}: the fixations on the head for the human video
were observed to more than that for the robot video ($F[1,54] = 12.7, p < .001$)

{\sf arms}: the fixations on the arms for the $\mathcal{H}$ video
were also greater than that for the robot video ($F[1,54] = 16.5, p < .01$)

{\sf legs}: the fixations on the legs were much lower
for the human video as compared to the robot video ($F[1,54] = 1.9, p < .1$)

{\sf torso}: the fixations on the torso were higher for the
human video than for the robot video ($F[1,54] = 2.65, p < .1$)

@@

We got a significant correlation between $\delta_{\mathcal{H},\mathcal{R}}$ and
the \anti. As can be seen in figure~\ref{h2}, there is a significant negative
correlation between the two quantities (Pearson Correlation Coefficient = -0.43,
$p < .001$).

@@

Based on ANOVA results, taking the 5 groups of AOIs {\sf head}, {\sf arms}, {\sf
hands}, {\sf torso}, {\sf legs} for the robot in both the shallow and deep
cognitive context conditions, the fixations on the head in the deep condition
were found to be significantly higher than that in the shallow condition
($F[1,54] = 4.2, p < .05$). For all other AOIs groups, the fixations across
shallow and deep conditions were almost the same. Figure~\ref{h3} shows the
distribution of proportion of time spent gazing on the 5 AOIs for the two
conditions.

@@

Running an ANOVA against the evolution of anthropomorphic attributions
(\deltaant) over the duration of the experiment, in the two cognitive
conditions, shows that \deltaant is greater for tasks with a deeper cognitive
context than that for the shallow cognitive tasks ($F[1,54] = 6.54, p < .05$,
figure~\ref{h4}). In other words, after being exposed to short videos of a robot
performing simple tasks, subjects primed with a deeper cognitive context report
a significantly higher tendency to anthropomorphize robots \emph{in general} (as
the questionnaires on anthropomorphic attributions explicitely refered to
\emph{robots in general}).
